The Country-level Impact of Educational Features on the Rate of Entrepreneurship - Data Gathering and Analysis

### 2014-11-13 GEMDataSource.Rmd
Update GEMDataSource.Rmd

>>>>

To measure these three dimensions of entrepreneurship, we will use three [Global Entrepreneurship Monitor (GEM)](http://www.gemconsortium.org) indicators:

- Established Business Ownership Rate (Percentage) 
- Nascent Entrepreneurship Rate (Percentage)
- Entrepreneurial intention Rate (Percentage)

We chose the GEM measure of entrepreneurship, as it is often referred to, especially in OECD studies.
